%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Leadership Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Residential College Advisor} % Job title
  {Yale-NUS College Residential College Advisor Program} % Organization
  {Singapore} % Location
  {May 2019 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Provided extensive support for international group of first-year
        students through academic issues, personal wellness, and crisis
        situations.}
    \item {Trained in conflict management and mediation, facilitating productive
      dialogue in diverse groups, and identity-based intersectional support.}
    \end{cvitems}
  }

  % \cventry
  % {Senior Student Associate / Tour Guide}
  % {Tours and Outreach Team, Yale-NUS College Admissions Office}
  % {Singapore}
  % {Aug. 2016 - Present}
  % {
  %   \begin{cvitems}
  %   \item {Co-managed a team of 27 Student Associates for the Admissions
  %       Office}
  %   \item {Conducted training and plan professional development opportunities for
  %       student tour guides}
  %   \end{cvitems}
  % }

  \cventry
  {Student Associate}
  {Residential Housing, Yale-NUS College Dean of Student's Office}
  {Singapore}
  {Aug. 2019 - Present}
  {
    \begin{cvitems}
    \item {Researched and prototyped automated method for allocating housing for
        first-year students and exchange students, who make up 30\% of total
        annual enrollment.}
    \item {Developed Python package for housing allocation which integrates into
        existing work-flow.}
    \end{cvitems}
  }
  \cventry
  {Captain / Advanced Training Director}
  {Yale-NUS Ballroom Society}
  {Singapore}
  {January 2019 - November 2019}
  {
    \begin{cvitems}
    \item {Led the biggest active student organization in Yale-NUS College, with
      67 members.}
    \item {Awarded ``Best Student Organization'' in the Kingfisher Awards 2019,
        an award ceremony organized by Yale-NUS College's Dean of Student's
        Office to recognise excellence in student organisations.}
    \item {Designed and executed training programs for both first-year dancers
        as well as advanced dancers.}
    \end{cvitems}
  }

\end{cventries}
%---------------------------------------------------------
%%% Local Variables:
%%% coding: utf-8
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-master: "../resume"
%%% End:
