%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Leadership Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Residential College Advisor} % Job title
  {Yale-NUS College Residential College Advisor Program} % Organization
  {Singapore} % Location
  {May 2019 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Provided extensive support for 10 local and international
        first-year students through academic issues, personal wellness, and
        crisis situations.}
    \item {Trained in conflict management and mediation, facilitating productive
      dialogue in diverse groups, and identity-based intersectional support.}
    \end{cvitems}
  }

  \cventry
  {Co-Manager / Training Head} % Job title
  {Yale-NUS Brewhouse: A Coffee Project} % Organization
  {Singapore} % Location
  {Jan. 2017 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Managed the operations and upkeep of the college's volunteer-run
        mobile cafe with a team of 31 student baristas.}
    \item {Improved operational workflow of the cart, including intuitive Google
      sheets order tracker for cashier use.}
    \end{cvitems}
  }

  \cventry
  {Senior Student Associate / Tour Guide}
  {Tours and Outreach Team, Yale-NUS College Admissions Office}
  {Singapore}
  {Aug. 2016 - Present}
  {
    \begin{cvitems}
    \item {Co-managed a team of 32 Student Associates for the Admissions
        Office.}
    \item {Conducted training, processed timesheets, and planned professional
        development opportunities for student tour guides.}
    \item{Represented the college in various university fairs and outreach
        sessions, with audiences ranging from prospective students to university
        counselors.}
    \end{cvitems}
  }

  \cventry
  {Captain / Advanced Training Director}
  {Yale-NUS Ballroom Society}
  {Singapore}
  {Jan. 2019 - Nov. 2019}
  {
    \begin{cvitems}
    \item {Led the biggest active student organization in Yale-NUS College, with
      67 members.}
    \item {Awarded ``Best Student Organization'' in the Kingfisher Awards 2019,
        an award ceremony organized by Yale-NUS College's Dean of Student's
        Office to recognise excellence in student organisations.}
    \item {Designed and executed training programs for both beginner and
        advanced dancers.}
    \end{cvitems}
  }

  \cventry
  {Class of 2020 Representative}
  {Yale-NUS College Student Government}
  {Singapore}
  {Jan. 2019 - Aug. 2019}
  {
    \begin{cvitems}
    \item {Represented the Class of 2020 in weekly senate meetings, advocating
        for topics such as attendance policies and student welfare.}
    \item {Proposed and passed senate resolution to establish a campus data
        office to better manage how the school handles student data and survey
        results.}
    \end{cvitems}
  }
  
  \cventry
  {Treasurer / Founding Member}
  {Community for Advocacy and Political Education (CAPE)}
  {Singapore}
  {Jan. 2017 - May 2018}
  {
    \begin{cvitems}
    \item {Built foundation for CAPE with students from Yale-NUS
        College and NUS Law.}
    \item {Designed workshops and online resources to increase political
        literacy and engagement amongst Singaporean youths.}
    \end{cvitems}
  }
  
  \cventry
  {Co-President}
  {RC\textsuperscript{3} (Yale-NUS College's Inter- and
    Intra-Residential College Event Co-ordinators)}
  {Singapore}
  {Jan. 2017 - May 2018}
  {
    \begin{cvitems}
    \item {Organised school-wide events for the college with the purpose of
        building the school community.}
    \item {Pioneered and aided in the transition of the Events Committee under
        the Dean of Student's Office, which has taken over the responsibility of
        event coordination.}
    \end{cvitems}
  }

  \cventry
  {Intercultural Peer Advisor}
  {Intercultural Peer Advisor Program, Yale-NUS College}
  {Singapore}
  {Nov. 2016 - May 2017}
  {
    \begin{cvitems}
    \item {Participated in social justice and cross-cultural communication
        training.}
    \item {Implemented projects with the Dean of Student’s Office that address
        discrimination and inter-group tension across campus.}
    \end{cvitems}
  }

\end{cventries}
%---------------------------------------------------------
%%% Local Variables:
%%% coding: utf-8
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-master: "../cv"
%%% End:
