% %-------------------------------------------------------------------------------
% %	SECTION TITLE
% %-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Research Team Lead} % Job title
  {Research Project on Computational Geometry and Animal Behaviour, Yale-NUS College} % Organization
  {Singapore} % Location
  {Starting in Jan. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Will begin leading a team of 6 Research Assistants on a project on
        \textit{Computational Geometric Techniques for Modelling Inherent Variability
        in Animal Behavior}, working with Professor Matthew Stamps and
        Professor Ajay Mathuru.}
    \end{cvitems}
  }
    
  \cventry
  {Bachelor's Thesis} % Job title
  {Linear Algebraic Techniques for Spanning Tree Enumeration} % Organization
  {Singapore} % Location
  {Aug. 2019 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Expanded on findings of the paper \textit{Linear Algebraic Techniques
          for Spanning Tree Enumeration} by Matthew T. Stamps, who is also
        supervising the thesis, and Steven Klee.}
    \item {Improved on the applications presented in the original paper, and
        defined a general characterization for graphs with a triangular rank-1
        augmented Laplacian matrix.}
    \item {Designed Python script for computational investigation on graphs that
        work well with the proposed method.}
    \end{cvitems}
  }
  
  \cventry
  {Research Intern} % Job title
  {CopeNLU, University of Copenhagen} % Organization
  {Copenhagen, Denmark} % Location
  {May 2019 - Jul. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Pioneered exploratory project investigating \textit{Zero-shot
          Relation Extraction with Graph Neural Networks}, with Professor
        Isabelle Augenstein, Selvan Raghavendra, and Johannes Bjerva.}
    \item {Developed and applied method for linking entities in existing
        zero-shot relation extraction dataset (Levy et al. 2018) to WikiData
        entries.}
    \item {Implemented a Graph Neural Network initialized with BERT embeddings
        of sentences (for edges) and node labels to predict unseen relations in
        a zero-shot setting.}
    \end{cvitems}
  }

\end{cventries}
%---------------------------------------------------------
%%% Local Variables:
%%% coding: utf-8
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-master: "../cv"
%%% End:
