%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Technical and Industry Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Student Associate}
  {Residential Housing, Yale-NUS College Dean of Student's Office}
  {Singapore}
  {Aug. 2019 - Present}
  {
    \begin{cvitems}
    \item {Researched and prototyped automated method for allocating housing for
        first-year students and exchange students, who make up 30\% of total
        annual enrollment.}
    \item {Modified Python implementation of Roth-Peranson algorithm to address
        the first-year housing problem in Yale-NUS College.}
    \item {Developed Python package for housing allocation which integrates into
        existing work-flow.}
    \end{cvitems}
  }

  \cventry
  {Summer Associate, Business System Analyst - Professional Services Team} % Job title
  {The Stakeholder Company} % Organization
  {Singapore} % Location
  {May 2018 - Jul. 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Built and pitched demo system for 6 figure deals with Google, UPS,
        Raffles Medical, and ExxonMobil.}
    \item {Fine tuned news monitoring systems in 10 local languages for
        Coca-Cola in ASEAN.}
    \item {Wrote SQL Scripts to optimise backend workflows including database
        search, result scoring, and short path finding.}
    \end{cvitems}
  }
    
  \cventry
  {Summer Intern} % Job title
  {SumoStory} % Organization
  {Singapore} % Location
  {Jun. 2017 - Aug. 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Built journalist profiling tool that determined journalist profile by
      applying topic modeling techniques to web-scraped articles written by the
      journalist.}
    \item {Designed internal journalist database, allowing for fast information
        retrieval, customer matching, and data entry.}
    \end{cvitems}
  }

\end{cventries}
%---------------------------------------------------------
%%% Local Variables:
%%% coding: utf-8
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-master: "../cv"
%%% End:
